---
title: "Specific State Graphs"
author: "Emily Axelsen"
date: "11/17/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(ggplot2)
library(dplyr)
library(readxl)
library(tidyverse)
```


```{r reading in data}
final_gun_violence_data <- readRDS("final data/final_data.rds")
state_policy <- readRDS("final data/state_policy.rds")
```

# David suggested I compare LA to Boston but my data doesn't back up 
# that there's a large difference in gun violence in the two cities.

```{r}
final_gun_violence_data %>%
  filter(state == "Massachusetts") %>%
  filter(city_or_county == "Boston") %>%
  nrow()
```

```{r}
final_gun_violence_data %>%
  filter(state == "California") %>%
  filter(city_or_county == "Los Angeles") %>%
  nrow()
```


# Registration required meaning: 
# Source https://lawcenter.giffords.org/gun-laws/policy-areas/gun-owner-responsibilities/registration/
# "Firearm registration laws require individuals to record their ownership of a firearm with a 
# designated law enforcement agency. These laws enable law enforcement to identify, disarm, and 
# prosecute violent criminals and people illegally in possession of firearms."

```{r}
registration <- state_policy %>%
  filter(w_guncontrol_registration_requir == "TRUE") 

# insert this line into graph?? Graph where registratration is required and resulting gun violence 
# versus registration not required and resulting gun violence

```











